\section{Method}
In this section you should explain what you have done, and how you have done it. The explanations should have enough detail to make a reproduction possible (i.e. it should be possible to do exactly what you have done, and receive the same results, only by doing what you write in this section).


It might be relevant to refer back to a part of theory, as explained in \autoref{subsec:theory_aSubsection}, to explain the design choices you made.

The method should answer the following questions:

How is your system implemented? Start by showing a block diagram of the system, then explain each block in more detail in the following subsections.

What tools and methods did you use to implement this? Explain as you go along. If you ran tests as part of the design process (i.e. to make decisions regarding implementation, and NOT those meant to verify/simulate the final circuit), they can be included where relevant in the following subsections.

\subsection{64 bit memory}
How are the bitcells connected to create the desired memory block?



\subsection{The bitcell}
Can you describe your bitcell implementation in detail? Why did you choose this circuit? Show at least a logic gate level figure of the bitcell, and figures showing each type of logic gate at the transistor level. Explain all your design choices.

How did you choose the values for width and length of the transistors? Why did you do it this way? Were there any considerations you had to make?

How did you choose the supply voltage? Why did you do it this way? Were there any considerations you had to make?



\subsection{FSM}
How did you create your FSM? Describe your steps from state diagram to finished circuit.

\subsection{The decoder (and/or any other blocks - one subsection for each block)}
Describe the implementation in detail. Why did you choose this circuit topology? Were there any considerations you had to make? Show at least a logic gate level figure.
